Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-16 TEBenchmarkPaper/article.tex
Existing evaluations

We make the assumption that each tool is intended to be \emph{general}, and
hence isn't hard-coded or fine-tuned to only perform well in a narrow domain.
Examples where this does \emph{not} hold include the natural number heuristics
of AM discussed in section~\ref{section:atf}, as well as machine learning models
trained on some specific dataset (such as this benchmark).

@@

The analyses in~\cite{claessen2013automating} took their definitions and ground
truths from the standard library of the Isabelle theorem prover: since the
library authors have gone to the effort of stating, proving and including these
theorems in every copy of their software, this is a good indication that they
are interesting.

Two tests were performed: one on a theory of natural numbers and one on a theory
of lists (whose definitions are shown in figure~\ref{figure:list_theory}). These
tests are limited both in number (it is difficult to draw general conclusions
from two datapoints) and by the small size of these theories (e.g. the natural
number theory from~\cite{Johansson.Dixon.Bundy:conjecture-generation} contains
only 4 definitions and 12 theorems).

We believe that this is a viable approach to drawing meaningful, objective
conclusions about such tools, but larger data sets are needed to judge
performance in different, especially \emph{novel}, domains (which, after all, is
the purpose of such tools). In addition, we might be concerned that such
``popular'' theories may be unrepresentative of typical usage. For example, we
would not expect the library functions in a typical verification problem to be
as mathematically rich as number theory.

>>>>

We make the assumption that each tool is intended to be \emph{general}, and
hence isn't hard-coded or fine-tuned to only perform well in a narrow domain.
Examples where this does \emph{not} hold include the natural number heuristics
of AM discussed in $\S$\ref{section:atf}, as well as machine learning models
trained on some specific dataset (such as the benchmark we describe).

@@

The analyses in~\cite{claessen2013automating} took their definitions and ground
truths from the standard library of the Isabelle proof assistant: since the
library authors have gone to the effort of stating, proving and including these
theorems in every copy of their software, this is a good indication that they
are interesting.

Tests were performed with a theory of natural numbers and a theory of lists (the
definitions shown in figure~\ref{figure:list_theory}), but it is difficult to
draw general conclusions from only two datapoints. These theories were also
quite small, the natural number theory
from~\cite{Johansson.Dixon.Bundy:conjecture-generation} only containing 4
definitions and 12 theorems.

Despite these limitations we believe that this is a viable approach to drawing
meaningful, objective conclusions about such tools; but only with larger data
sets can we judge performance in different, especially \emph{novel}, domains
(which, after all, is the purpose of such tools). In addition, we might be
concerned that such ``popular'' theories may be unrepresentative of typical
usage. For example, we would not expect the library functions in a typical
verification problem to be as mathematically rich as number theory.
